Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-13 paper/sec-analysis.tex
plots for the paper

\subsubsection{Boosted category}

We begin with the boosted category, which is the one that leads
to a higher signal significance.
%
First of all,
in Fig.~\ref{fig:cutplots1} we show
the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.
  %
  We see that the background distribution
  falls off rather steeply than the signal, therefore
  suggesting that the boosted region should be
  advantageous to suppress the background.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.48\textwidth]{plots/pt_H0_res_C1_boost.pdf}
  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1_boost.pdf}
\caption{\small Left plot: the $p_T$ distribution of the
  leading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  All distributions have been normalized to their total integral.
  %
  Right plot: the invariant mass of the leading Higgs
  candidate.
}
\label{fig:cutplots1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Resolved category}

@@

>>>>

We will compare kinematic variables at each step of the analysis
for the boosted and for the resolved categories.
%
The corresponding plots for the intermediate category can be found in the webpage
mentioned above.
%
In the following comparisons, we compare related
kinematical distributions in the two categories.

First of all,
in Fig.~\ref{fig:cutplots1} we show
the $p_T$ distribution of the 
of the
  leading and subleading large-$R$ jet in the boosted category, comparing
  the shapes of the distribution in signal and background events.
  %
  As we will do in all this section,
  all distributions have been normalized to their total integral.
  %
  We see that the background distribution
  falls off rather steeply than the signal, therefore
  suggesting that the boosted region should be
  advantageous to suppress the background.
  %
  This is true both for the leading and the subleading
  large-$R$ jets.
  %
  These distributions justify our choice of $p_T \ge 200$ GeV
  for the large-$R$ jets in the boosted category.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
 \includegraphics[width=0.48\textwidth]{plots/pt_H0_boost_C1.pdf}
 \includegraphics[width=0.48\textwidth]{plots/pt_H1_boost_C1.pdf}
\caption{\small  The $p_T$ distribution of the
  leading (left plot) and
  subleading (right plot) large-$R$ jet in the boosted category.
  %
  We comparing
  the shapes of the distribution in signal and background events,
  where both
  distributions have been normalized to their total integral.
}
\label{fig:cutplots1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

Next in Fig.~\ref{fig:mHHinv} we show the invariant mass
of the leading Higgs candidates, before the Higgs mass window
cut is applied, for the resolved and boosted categories.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1.pdf}
  \includegraphics[width=0.48\textwidth]{plots/m_H0_boost_C1.pdf}
  \caption{\small The invariant mass distribution of the leading
    Higgs candidates on the resolved (left plot) and boosted (right
    plot) categories.
}
\label{fig:mHHinv}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
